Energy spectrum of diatomic molecules\\ in the Quantum Drude Oscillator model

### 2022-07-05 paper/main.tex
paper

    A Quantum Drude Oscillator (QDO) is a very simple atomistic model in which the properties of an atom are encompassed in a small number of parameters. The model consists in assimilating the atom to a point particle of mass $m$ and electric charge $-q$ attached to a fixed (infinite mass) center of charge $+q$ by a harmonic spring characterized by a frequency $\omega$. Molecules are then defined as a collections of QDOs interactig through Coulomb interactions.

@@

    By truncating the multipolar expansion up to Dipole-Dipole, one obtain a quadratic Hamiltonian, hence the quantum Hamiltonian can be analytically diagonalized. Though simple, this system was shown to capture long-range phenomena in large atomistic systems \cite{https://doi.org/10.48550/arxiv.2205.11549}.

>>>>

    MBD, non-covalent interaction, linear response,

    A Quantum Drude Oscillator (QDO) is a minimalistic atomistic model in which the properties of an atom are encompassed in a small number of parameters. The model consists in assimilating the atom to a point particle of mass $m$ and electric charge $-q$ attached to a fixed (infinite mass) center of charge $+q$ by a harmonic spring characterized by a frequency $\omega$. Molecules are then defined as a collections of QDOs interacting through Coulomb interactions.

@@

    By truncating the multipolar expansion up to Dipole-Dipole, one obtains a quadratic Hamiltonian. In the case of a closed linear chain, one can analytically solve for the spectrum of the Hamiltonion \cite{doi:10.1063/1.1743992}. In the case of a general geometry, one can solve for the London-van der Waals interaction energy can be calculated through a perturbative approach \cite{doi:10.1063/1.1743991}. Though simple, this system was shown to capture long-range phenomena in large biomolecular systems \cite{https://doi.org/10.48550/arxiv.2205.11549}.
